Cryptanalysis of \MORUS

### 2018-05-11 morusAC_08_Conclusion.tex
ePrint version: author names + acknowledgments + increased margins
Acknowledgement

>>>>

\ifanonymous
\else
\section{Acknowledgments}

The results presented here were originally found during the Flexible
Symmetric Cryptography workshop held at the Lorentz Center in Leiden,
Netherlands.  The authors would like to thank Meltem Sonmez Turan who
participated to the initial discussion.  The fifth author was
supported by EPSRC Grant EP/M013472/1.  The fouth and sixth authors
are partially supported by the French Agence Nationale de la Recherche
through the BRUTUS project under Contract ANR-14-CE28-0015.

\fi

\FloatBarrier
